Positive Results in Registered Reports

### 2020-01-11 manuscript/manuscript.tex
Adjusted formatting to make the manuscript work in journal mode. Caution: I installed the development branch of papaja to allow column-spanning tables!

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[british,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Positive Results in Registered Reports},
            pdfauthor={Anne Scheel, Mitchell Schijen, \& Daniël Lakens},
            pdfkeywords={keyword 1, keyword 2, keyword 3},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\shorttitle{Positive Results in Registered Reports}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Eindhoven University of Technology}
\keywords{keyword 1, keyword 2, keyword 3\newline\indent Word count: XXX}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\usepackage{lineno}

\linenumbers
\usepackage{float}
\usepackage{framed}
\usepackage{caption}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1, footnotesize}}
\captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
\newfloat{textbox}{thp}{lop}
\floatname{textbox}{Box}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=british]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[variant=british]{english}
\fi

\title{Positive Results in Registered Reports}
\author{Anne Scheel\textsuperscript{1}, Mitchell Schijen\textsuperscript{1}, \& Daniël Lakens\textsuperscript{1}}
\date{}

\authornote{

Correspondence concerning this article should be addressed to Anne Scheel, Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands. E-mail: \href{mailto:a.m.scheel@tue.nl}{\nolinkurl{a.m.scheel@tue.nl}}}
\note{\clearpage}
\abstract{
XXXXXXXXXXXXXXXXXXX

@@

\begin{figure}
\includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{Sampling process and exclusions for standard reports and Registered Reports. Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded. \enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: Four of these had been treated as RRs but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance. We chose to exclude these cases to be conservative.}\label{fig:sampling}
\end{figure}

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-4}Positive results in original studies vs replication studies}
\begin{tabular}{lrrrrrrrr}
\toprule
 & \multicolumn{4}{c}{original studies} & \multicolumn{4}{c}{replication studies} \\
\cmidrule(r){2-5} \cmidrule(r){6-9}
 & n & supported & \% & 95\% CI & n & supported & \% & 95\% CI\\
\midrule
SRs & 148 & 142 & 95.95 & 91.39; 98.50 & 4 & 4 & 100.00 & 39.76; 100.00\\
RRs & 30 & 15 & 50.00 & 31.30; 68.70 & 41 & 16 & 39.02 & 24.20; 55.50\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} SRs = standard reports, RRs = Registered Reports}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-6}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}
\footnotesize{
\begin{tabular}{llrrr}
\toprule
 &  & \multicolumn{3}{c}{source} \\
\cmidrule(r){3-5}
core word(s) & introduction phrase & abstract & full text & total\\
\midrule
hypothes* &  & 5 & 12 & 17\\
 & (Hypothesis 1) & 0 & 1 & 1\\
 & Hypothesis 1 (H1): & 0 & 2 & 2\\
 & Hypothesis 1: & 0 & 1 & 1\\
 & Hypothesis 1a (H1a): & 0 & 1 & 1\\
 & hypothesis was & 0 & 1 & 1\\
 & Hypothesis: & 0 & 1 & 1\\
 & hypothesize that & 0 & 3 & 3\\
 & hypothesized that & 4 & 2 & 6\\
 & registered ... hypotheses & 1 & 0 & 1\\ \midrule
hypothes*, test* &  & 3 & 2 & 5\\
 & test of ... hypotheses & 0 & 1 & 1\\
 & test of ... hypothesis & 1 & 0 & 1\\
 & test the hypothesis that & 1 & 0 & 1\\
 & tested ... hypotheses & 0 & 1 & 1\\
 & tested the hypothesis that & 1 & 0 & 1\\ \midrule
test* &  & 5 & 2 & 7\\
 & test if & 0 & 1 & 1\\
 & test whether & 1 & 1 & 2\\
 & tested whether & 2 & 0 & 2\\
 & testing & 1 & 0 & 1\\
 & to ... test & 1 & 0 & 1\\ \midrule
test*, predict* & test ... prediction & 0 & 1 & 1\\ \midrule
examin* &  & 5 & 0 & 5\\
 & examine whether & 2 & 0 & 2\\
 & examined & 1 & 0 & 1\\
 & examined whether & 1 & 0 & 1\\
 & to examine & 1 & 0 & 1\\ \midrule
predict* &  & 4 & 0 & 4\\
 & had ... predictions & 1 & 0 & 1\\
 & predicted that & 2 & 0 & 2\\
 & predicts that & 1 & 0 & 1\\ \midrule
(other) &  & 0 & 5 & 5\\
 & (H1) & 0 & 1 & 1\\
 & expected that & 0 & 1 & 1\\
 & if ... then & 0 & 1 & 1\\
 & predication that & 0 & 1 & 1\\
 & we expect & 0 & 1 & 1\\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} Table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-7}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
\scriptsize{
\begin{tabular}{lllrrrr}
\toprule
 &  &  & \multicolumn{3}{c}{source}  &\\
\cmidrule(r){4-6}
 & core word(s) & introduction phrase & abstract & full text & total & \\
\midrule
 & hypothes* &  & 2 & 5 & 7 & \\
 &  & according to ... hypothesis & 0 & 1 & 1 & \\
 &  & Hypotheses & 0 & 1 & 1 & \\
 &  & Hypothesis 1 (H1): & 0 & 1 & 1 & \\
 &  & hypothesize that & 0 & 1 & 1 & \\
 &  & hypothesized that & 2 & 1 & 3 & \\ \midrule
 & hypothes*, test* &  & 2 & 1 & 3 & \\
 &  & test ... hypotheses & 0 & 1 & 1 & \\
 &  & test ... hypothesis & 1 & 0 & 1 & \\
 &  & tested ... hypotheses & 1 & 0 & 1 & \\ \midrule
 & hypothes*, examin* & examined ... hypothesis & 1 & 0 & 1 & \\ \midrule
 & hypothes*, predict* & hypotheses predicted & 1 & 0 & 1 & \\ \midrule
 & replicat* &  & 20 & 3 & 23 & \\
 &  & aim ... to replicate & 0 & 1 & 1 & \\
 &  & aim at replicating & 1 & 0 & 1 & \\
 &  & aimed to replicate & 0 & 1 & 1 & \\
 &  & attempted to replicate & 1 & 0 & 1 & \\
 &  & attempts to replicate & 1 & 0 & 1 & \\
 &  & conducted ... replication & 3 & 0 & 3 & \\
 &  & conducted ... replications & 2 & 0 & 2 & \\
 &  & performed ... replication & 2 & 0 & 2 & \\
 &  & present ... replication & 1 & 0 & 1 & \\
 &  & present ... replications & 1 & 0 & 1 & \\
 &  & replicated ... experiment & 1 & 0 & 1 & \\
 &  & replicating & 0 & 1 & 1 & \\
 &  & report ... replication attempt & 1 & 0 & 1 & \\
 &  & report ... replications & 2 & 0 & 2 & \\
 &  & sought to replicate & 3 & 0 & 3 & \\
 &  & we replicated & 1 & 0 & 1 & \\ \midrule
 & replicat*, examin* & critically examine and replicate & 1 & 0 & 1 & \\ \midrule
 & test* &  & 4 & 0 & 4 & \\
 &  & testing whether & 2 & 0 & 2 & \\
 &  & to ... test & 1 & 0 & 1 & \\
 &  & to test & 1 & 0 & 1 & \\ \midrule
 & examin* & examine whether & 0 & 1 & 1 & \\ \midrule
 & predict* & predicted that & 2 & 0 & 2 & \\ \midrule
 & (other) &  & 4 & 6 & 10 & \\
 &  & establish whether & 0 & 1 & 1 & \\
 &  & H1 & 0 & 2 & 2 & \\
 &  & investigate if & 1 & 0 & 1 & \\
 &  & sought to reproduce & 1 & 0 & 1 & \\
 &  & suggests that & 2 & 0 & 2 & \\
 &  & we ... conducted & 0 & 1 & 1 & \\
 &  & we assume & 0 & 1 & 1 & \\
 &  & we expect & 0 & 1 & 1 & \\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} Table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no hypothesis introduction. Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/powerbaserate-1.pdf}
\caption{\label{fig:powerbaserate}(ref:powerbaserate}
\end{figure}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Agnoli2017}{}%
Agnoli, F., Wicherts, J. M., Veldkamp, C. L. S., Albiero, P., \& Cubelli, R. (2017). Questionable research practices among italian research psychologists. \emph{PLOS ONE}, \emph{12}(3), e0172792. doi:\href{https://doi.org/10.1371/journal.pone.0172792}{10.1371/journal.pone.0172792}

\leavevmode\hypertarget{ref-Allen2019}{}%
Allen, C., \& Mehler, D. M. A. (2019). Open science challenges, benefits and tips in early career and beyond. \emph{PLOS Biology}, \emph{17}(5), e3000246. doi:\href{https://doi.org/10.1371/journal.pbio.3000246}{10.1371/journal.pbio.3000246}

\leavevmode\hypertarget{ref-Atkinson1982}{}%
Atkinson, D. R., Furlong, M. J., \& Wampold, B. E. (1982). Statistical significance, reviewer evaluations, and the scientific process: Is there a (statistically) significant relationship? \emph{Journal of Counseling Psychology}, \emph{29}(2), 189--194. doi:\href{https://doi.org/10.1037/0022-0167.29.2.189}{10.1037/0022-0167.29.2.189}

@@

\leavevmode\hypertarget{ref-Chambers2015}{}%
Chambers, C., Dienes, Z., McIntosh, R., Rotshtein, P., \& Willmes, K. (2015). Registered Reports: Realigning incentives in scientific publishing. \emph{Cortex}, \emph{66}, 1--2. doi:\href{https://doi.org/10.1016/j.cortex.2015.03.022}{10.1016/j.cortex.2015.03.022}

\leavevmode\hypertarget{ref-OSC2015}{}%
Collaboration, O. S. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716. doi:\href{https://doi.org/10.1126/science.aac4716}{10.1126/science.aac4716}

\leavevmode\hypertarget{ref-Cristea2018}{}%
Cristea, I. A., \& Ioannidis, J. P. A. (2018). P values in display items are ubiquitous and almost invariably significant: A survey of top science journals. \emph{PLOS ONE}, \emph{13}(5), e0197440. doi:\href{https://doi.org/10.1371/journal.pone.0197440}{10.1371/journal.pone.0197440}

\leavevmode\hypertarget{ref-Fanelli2010}{}%
Fanelli, D. (2010). "Positive" results increase down the hierarchy of the sciences. \emph{PLoS ONE}, \emph{5}(4), e10068. doi:\href{https://doi.org/10.1371/journal.pone.0010068}{10.1371/journal.pone.0010068}

\leavevmode\hypertarget{ref-Fanelli2012}{}%
Fanelli, D. (2012). Negative results are disappearing from most disciplines and countries. \emph{Scientometrics}, \emph{90}(3), 891--904. doi:\href{https://doi.org/10.1007/s11192-011-0494-7}{10.1007/s11192-011-0494-7}

>>>>

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[british,,jou,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Positive Results in Registered Reports},
            pdfkeywords={keyword 1, keyword 2, keyword 3},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

% Manuscript styling
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Positive Results in Registered Reports}
\author{Anne Scheel\textsuperscript{1}, Mitchell Schijen\textsuperscript{1}, \& Daniël Lakens\textsuperscript{1}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Eindhoven University of Technology}
\authornote{

Correspondence concerning this article should be addressed to Anne Scheel, Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands. E-mail: a.m.scheel@tue.nl}
\note{\textbackslash{}clearpage}
\keywords{keyword 1, keyword 2, keyword 3\newline\indent Word count: XXX}
\usepackage{dblfloatfix}

\usepackage{float}
\usepackage{framed}
\usepackage{caption}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1, small}, skip=11pt}
\captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
\newfloat{textbox}{thp}{lop}
\floatname{textbox}{Box}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=british]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[variant=british]{english}
\fi

\title{Positive Results in Registered Reports}

\date{}

\abstract{
XXXXXXXXXXXXXXXXXXX
}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{Sampling process and exclusions for standard reports and Registered Reports. Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded. \enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: Four of these had been treated as RRs but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance. We chose to exclude these cases to be conservative.}\label{fig:sampling}
\end{figure*}

@@

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-4}Positive results in original studies vs replication studies}

\begin{tabular}{lrrrrrrrr}
\toprule
 & \multicolumn{4}{c}{original studies} & \multicolumn{4}{c}{replication studies} \\
\cmidrule(r){2-5} \cmidrule(r){6-9}
 & n & supported & \% & 95\% CI & n & supported & \% & 95\% CI\\
\midrule
SRs & 148 & 142 & 95.95 & 91.39; 98.50 & 4 & 4 & 100.00 & 39.76; 100.00\\
RRs & 30 & 15 & 50.00 & 31.30; 68.70 & 41 & 16 & 39.02 & 24.20; 55.50\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} SRs = standard reports, RRs = Registered Reports}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table*}

@@

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-6}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}

\footnotesize{

\begin{tabular}{llrrr}
\toprule
 &  & \multicolumn{3}{c}{source} \\
\cmidrule(r){3-5}
core word(s) & introduction phrase & abstract & full text & total\\
\midrule
hypothes* &  & 5 & 12 & 17\\
 & (Hypothesis 1) & 0 & 1 & 1\\
 & Hypothesis 1 (H1): & 0 & 2 & 2\\
 & Hypothesis 1: & 0 & 1 & 1\\
 & Hypothesis 1a (H1a): & 0 & 1 & 1\\
 & hypothesis was & 0 & 1 & 1\\
 & Hypothesis: & 0 & 1 & 1\\
 & hypothesize that & 0 & 3 & 3\\
 & hypothesized that & 4 & 2 & 6\\
 & registered ... hypotheses & 1 & 0 & 1\\ \midrule
hypothes*, test* &  & 3 & 2 & 5\\
 & test of ... hypotheses & 0 & 1 & 1\\
 & test of ... hypothesis & 1 & 0 & 1\\
 & test the hypothesis that & 1 & 0 & 1\\
 & tested ... hypotheses & 0 & 1 & 1\\
 & tested the hypothesis that & 1 & 0 & 1\\ \midrule
test* &  & 5 & 2 & 7\\
 & test if & 0 & 1 & 1\\
 & test whether & 1 & 1 & 2\\
 & tested whether & 2 & 0 & 2\\
 & testing & 1 & 0 & 1\\
 & to ... test & 1 & 0 & 1\\ \midrule
test*, predict* & test ... prediction & 0 & 1 & 1\\ \midrule
examin* &  & 5 & 0 & 5\\
 & examine whether & 2 & 0 & 2\\
 & examined & 1 & 0 & 1\\
 & examined whether & 1 & 0 & 1\\
 & to examine & 1 & 0 & 1\\ \midrule
predict* &  & 4 & 0 & 4\\
 & had ... predictions & 1 & 0 & 1\\
 & predicted that & 2 & 0 & 2\\
 & predicts that & 1 & 0 & 1\\ \midrule
(other) &  & 0 & 5 & 5\\
 & (H1) & 0 & 1 & 1\\
 & expected that & 0 & 1 & 1\\
 & if ... then & 0 & 1 & 1\\
 & predication that & 0 & 1 & 1\\
 & we expect & 0 & 1 & 1\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table*}

\begin{table*}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-7}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}

\footnotesize{

\begin{tabular}{lllrrrr}
\toprule
 &  &  & \multicolumn{3}{c}{source}  &\\
\cmidrule(r){4-6}
 & core word(s) & introduction phrase & abstract & full text & total & \\
\midrule
 & hypothes* &  & 2 & 5 & 7 & \\
 &  & according to ... hypothesis & 0 & 1 & 1 & \\
 &  & Hypotheses & 0 & 1 & 1 & \\
 &  & Hypothesis 1 (H1): & 0 & 1 & 1 & \\
 &  & hypothesize that & 0 & 1 & 1 & \\
 &  & hypothesized that & 2 & 1 & 3 & \\ \midrule
 & hypothes*, test* &  & 2 & 1 & 3 & \\
 &  & test ... hypotheses & 0 & 1 & 1 & \\
 &  & test ... hypothesis & 1 & 0 & 1 & \\
 &  & tested ... hypotheses & 1 & 0 & 1 & \\ \midrule
 & hypothes*, examin* & examined ... hypothesis & 1 & 0 & 1 & \\ \midrule
 & hypothes*, predict* & hypotheses predicted & 1 & 0 & 1 & \\ \midrule
 & replicat* &  & 20 & 3 & 23 & \\
 &  & aim ... to replicate & 0 & 1 & 1 & \\
 &  & aim at replicating & 1 & 0 & 1 & \\
 &  & aimed to replicate & 0 & 1 & 1 & \\
 &  & attempted to replicate & 1 & 0 & 1 & \\
 &  & attempts to replicate & 1 & 0 & 1 & \\
 &  & conducted ... replication & 3 & 0 & 3 & \\
 &  & conducted ... replications & 2 & 0 & 2 & \\
 &  & performed ... replication & 2 & 0 & 2 & \\
 &  & present ... replication & 1 & 0 & 1 & \\
 &  & present ... replications & 1 & 0 & 1 & \\
 &  & replicated ... experiment & 1 & 0 & 1 & \\
 &  & replicating & 0 & 1 & 1 & \\
 &  & report ... replication attempt & 1 & 0 & 1 & \\
 &  & report ... replications & 2 & 0 & 2 & \\
 &  & sought to replicate & 3 & 0 & 3 & \\
 &  & we replicated & 1 & 0 & 1 & \\ \midrule
 & replicat*, examin* & critically examine and replicate & 1 & 0 & 1 & \\ \midrule
 & test* &  & 4 & 0 & 4 & \\
 &  & testing whether & 2 & 0 & 2 & \\
 &  & to ... test & 1 & 0 & 1 & \\
 &  & to test & 1 & 0 & 1 & \\ \midrule
 & examin* & examine whether & 0 & 1 & 1 & \\ \midrule
 & predict* & predicted that & 2 & 0 & 2 & \\ \midrule
 & (other) &  & 4 & 6 & 10 & \\
 &  & establish whether & 0 & 1 & 1 & \\
 &  & H1 & 0 & 2 & 2 & \\
 &  & investigate if & 1 & 0 & 1 & \\
 &  & sought to reproduce & 1 & 0 & 1 & \\
 &  & suggests that & 2 & 0 & 2 & \\
 &  & we ... conducted & 0 & 1 & 1 & \\
 &  & we assume & 0 & 1 & 1 & \\
 &  & we expect & 0 & 1 & 1 & \\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no hypothesis introduction. Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table*}

@@

\begin{figure*}

{\centering \includegraphics[width=0.6\textwidth]{manuscript_files/figure-latex/powerbaserate-1}

\caption{Combinations of the proportion of true hypotheses and statistical power that would produce the observed positive result rates given \(\alpha = 5 \%\) and no bias. Shaded areas indicate \(95\%\) confidence intervals. SRs = standard reports, RRs = Registered Reports. The curve for all SRs (i.e, including replications; \(96.05 \%\) positive results, \(N = 152\)) is not shown because it is almost identical to the one for original SRs. Plotted values were calculated using the equation \(PRR = \alpha*(1-t) + (1-\beta)*t\); with \(PRR =\) positive result rate, \(\alpha =\) probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), \(1-\beta =\) probability of obtaining a positive result when testing a true hypothesis (power), and \(t =\) proportion of true hypotheses; and solving for \(t\) and \(1-\beta\), respectively.}\label{fig:powerbaserate}
\end{figure*}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Agnoli2017}{}%
Agnoli, F., Wicherts, J. M., Veldkamp, C. L. S., Albiero, P., \& Cubelli, R. (2017). Questionable research practices among italian research psychologists. \emph{PLOS ONE}, \emph{12}(3), e0172792. \url{https://doi.org/10.1371/journal.pone.0172792}

\leavevmode\hypertarget{ref-Allen2019}{}%
Allen, C., \& Mehler, D. M. A. (2019). Open science challenges, benefits and tips in early career and beyond. \emph{PLOS Biology}, \emph{17}(5), e3000246. \url{https://doi.org/10.1371/journal.pbio.3000246}

\leavevmode\hypertarget{ref-Atkinson1982}{}%
Atkinson, D. R., Furlong, M. J., \& Wampold, B. E. (1982). Statistical significance, reviewer evaluations, and the scientific process: Is there a (statistically) significant relationship? \emph{Journal of Counseling Psychology}, \emph{29}(2), 189--194. \url{https://doi.org/10.1037/0022-0167.29.2.189}

@@

\leavevmode\hypertarget{ref-Chambers2015}{}%
Chambers, C., Dienes, Z., McIntosh, R., Rotshtein, P., \& Willmes, K. (2015). Registered Reports: Realigning incentives in scientific publishing. \emph{Cortex}, \emph{66}, 1--2. \url{https://doi.org/10.1016/j.cortex.2015.03.022}

\leavevmode\hypertarget{ref-OSC2015}{}%
Collaboration, O. S. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716. \url{https://doi.org/10.1126/science.aac4716}

\leavevmode\hypertarget{ref-Cristea2018}{}%
Cristea, I. A., \& Ioannidis, J. P. A. (2018). P values in display items are ubiquitous and almost invariably significant: A survey of top science journals. \emph{PLOS ONE}, \emph{13}(5), e0197440. \url{https://doi.org/10.1371/journal.pone.0197440}

\leavevmode\hypertarget{ref-Fanelli2010}{}%
Fanelli, D. (2010). "Positive" results increase down the hierarchy of the sciences. \emph{PLoS ONE}, \emph{5}(4), e10068. \url{https://doi.org/10.1371/journal.pone.0010068}

\leavevmode\hypertarget{ref-Fanelli2012}{}%
Fanelli, D. (2012). Negative results are disappearing from most disciplines and countries. \emph{Scientometrics}, \emph{90}(3), 891--904. \url{https://doi.org/10.1007/s11192-011-0494-7}

\leavevmode\hypertarget{ref-Fiedler2016}{}%
Fiedler, K., \& Schwarz, N. (2016). Questionable Research Practices Revisited. \emph{Social Psychological and Personality Science}, \emph{7}(1), 45--52. \url{https://doi.org/10.1177/1948550615612150}
